Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2019-11-12 Silvers_cfmip_draft.tex
added the HML_CF_cfmip_bias.eps figure and a brief description

>>>>

\begin{figure}
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/HML_CF_cfmip.eps}
  \caption{Cloud fraction from several of the CMIP6 experiments.}
  \label{fig:cf_hml_manyexps}
\end{figure}

\begin{figure}
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/HML_CF_cfmip_bias.eps}
  \caption{Cloud fraction from several of the CMIP6 experiments.}
  \label{fig:cf_hml_bias}
\end{figure}

Plotting the cloud fields as a function of latitude and height highlights some of the similarities and differences 
between the various experiments.  In general the clouds in the amip and historical simulations are similar to 
each other, as we would expect.  The differences between the clouds of these experiments are due to the 
different SST pattern that the two experiments have.  We can thus see how the clouds change as a result 
of SST biases over the observational period.  Two warming experiments have been plotted, amip p4K and 
the coupled abrupt 4xCO2 experiment.  The cloud fields in these experiments are similar to each other, with 
the differences again likely coming from the different SST patterns that result from a fully coupled system.  The 
cooling experiment is rather unique and tends to have cloud fraction changes in the opposite direction as 
the warming experiments.
